Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-10 delegations.tex
Fix typo

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate and measure the result by interacting with the prover.
\end{definition}

>>>>

\begin{definition}
	A \emph{quantum delegation protocol} is an polynomial-round interactive protocol between a BPP verifier and a BQP prover. The BPP verifier has an arbitrary quantum circuit with classical input that it needs to evaluate and measure the result of by interacting with the prover.
\end{definition}
